plotly charts for sensitivity iteractive explorer html

### 2025-11-28 report_plotlyCharts.Rmd

# df_beforeFilter <- df_beforeFilter %>%
#   filter(tgt2030 != 59)
# df <- df %>%
#   filter(tgt2030 != 59)

@@

  plotData <- df_beforeFilter %>%
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
           value = currencyConversion*value) %>%
    mutate(value = round(value,2))

@@

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`emiIntTrnsp`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr") %>%
    calc_addVariable( "`emiIntraEU`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr") %>%
    filter(variable %in% c("emiIntTrnsp","emiIntraEU")) %>%
    pivot_wider(names_from = variable, values_from = value) %>%
    mutate(ref_emiIntTrnsp = tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference),
           ref_emiIntraEU = tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) %>%
    mutate(red_emiIntTrnsp = emiIntTrnsp/ref_emiIntTrnsp,
           red_emiIntraEU = emiIntraEU/ref_emiIntraEU) %>%
    mutate(value = emiIntTrnsp,
           reduction = ifelse(period >= 2045, red_emiIntTrnsp, red_emiIntraEU)) %>%
    mutate(text = paste0("Emissions: ", round(value), " Mt CO2/yr", "\nReduction: ", round(1-reduction,3)*100, "%", "\nPeriod: ", period, "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim)) %>%
    mutate(value = round(value,2))

@@

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>%
    mutate(value = round(value,2))

@@

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>%
    mutate(sector = factor(invertVars[as.character(variable)], c("Total", "Transport", "Industry", "Buildings"))) %>%
    mutate(value = round(value,4))

@@

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>%
    mutate(type = gsub("\\d$", "", as.character(invertVars[as.character(variable)]))) %>%
    group_by(model,scenario,region,unit,period,type,tgt2030,lim) %>%
    summarize(value=sum(value),.groups = "keep") %>%
    mutate(type=factor(type, levels=unique(gsub("\\d$", "", names(vars))))) %>%
    mutate(value = round(value,2))

@@

  plotData <- df_beforeFilter %>%
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(value = round(value,2))

@@

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(sector = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value,2))

@@

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(pe = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value,2))

@@

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(seel = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value * 1/0.0036))

@@

<!--   plotData <- df_beforeFilter %>%  -->
<!--     filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>% -->
<!--     calc_addVariable( "`emiIntTrnsp`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr") %>% -->
<!--     calc_addVariable( "`emiIntraEU`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr") %>% -->
<!--     filter(variable %in% c("emiIntTrnsp","emiIntraEU")) %>% -->
<!--     pivot_wider(names_from = variable, values_from = value) %>% -->
<!--     mutate(ref_emiIntTrnsp = tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference), -->
<!--            ref_emiIntraEU = tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) %>% -->
<!--     mutate(red_emiIntTrnsp = emiIntTrnsp/ref_emiIntTrnsp, -->
<!--            red_emiIntraEU = emiIntraEU/ref_emiIntraEU) %>% -->
<!--     mutate(value = emiIntTrnsp, -->
<!--            reduction = ifelse(period >= 2045, red_emiIntTrnsp, red_emiIntraEU)) %>% -->
<!--     mutate(text = paste0("Emissions: ", round(value), " Mt CO2/yr", "\nReduction: ", round(1-reduction,3)*100, "%", "\nPeriod: ", period, "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim)) %>% -->
<!--     mutate(value = round(value,2)) -->

@@

<!-- # # Final Energy -->
<!-- # vars <- c( -->
<!-- #   "Electricity" = "FE|Electricity", -->
<!-- #   "Heat" = "FE|Heat", -->
<!-- #   "Hydrogen" = "FE|Hydrogen", -->
<!-- #   "Gases" = "FE|Gases", -->
<!-- #   #"Gases" = "FE|Gases|Biomass", -->
<!-- #   #"Gases" = "FE|Gases|Hydrogen", -->
<!-- #   #"Gases" = "FE|Gases|Fossil", -->
<!-- #   "Liquids" = "FE|Liquids", -->
<!-- #   #"Liquids" = "FE|Liquids|Biomass", -->
<!-- #   #"Liquids" = "FE|Liquids|Hydrogen", -->
<!-- #   #"Liquids" = "FE|Liquids|Fossil", -->
<!-- #   "Solids" = "FE|Solids"	 -->
<!-- #   #"Solids" = "FE|Solids|Biomass",	 -->
<!-- #   #"Solids" = "FE|Solids|Fossil"	 -->
<!-- # ) -->
<!-- #  -->
<!-- # invertVars <- setNames(names(vars),vars) -->
<!-- #  -->
<!-- # plotData <- df_beforeFilter %>%  -->
<!-- #   filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% vars) %>% -->
<!-- #   mutate(fe = factor(invertVars[as.character(variable)], names(vars))) -->
<!-- #  -->
<!-- # g[["finalEnergy"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) + -->
<!-- #     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
<!-- #     geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
<!-- #     geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) + -->
<!-- #     facet_wrap(~ fe, nrow=2) + -->
<!-- #     scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) +  -->
<!-- #     scale_color_manual(values = scenarioColor) +  -->
<!-- #     scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) + -->
<!-- #     scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) + -->
<!-- #     theme_doubleColumn() + -->
<!-- #     theme(legend.position = "none") + -->
<!-- #     theme(axis.title.y=element_blank())  -->
<!-- #  -->
<!-- # plotly2js( -->
<!-- #   ggplotly(ggplotly(g[["finalEnergy"]])) %>% layout(autosize = TRUE), -->
<!-- #              div.id = "finalEnergy", output.html = TRUE, output.file = "finalEnergy.js",  -->
<!-- #              output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/finalEnergy.html")) -->

>>>>

@@

  plotData <- df %>%
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
           value = currencyConversion*value) %>%
    mutate(value = round(value,2))

@@

  plotData <- df %>% 
    filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`emiIntTrnsp`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr") %>%
    calc_addVariable( "`emiIntraEU`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr") %>%
    filter(variable %in% c("emiIntTrnsp","emiIntraEU")) %>%
    pivot_wider(names_from = variable, values_from = value) %>%
    mutate(ref_emiIntTrnsp = tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference),
           ref_emiIntraEU = tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) %>%
    mutate(red_emiIntTrnsp = emiIntTrnsp/ref_emiIntTrnsp,
           red_emiIntraEU = emiIntraEU/ref_emiIntraEU) %>%
    mutate(value = emiIntTrnsp,
           reduction = ifelse(period >= 2045, red_emiIntTrnsp, red_emiIntraEU)) %>%
    mutate(text = paste0("Emissions: ", round(value), " Mt CO2/yr", "\nReduction: ", round(1-reduction,3)*100, "%", "\nPeriod: ", period, "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim)) %>%
    mutate(value = round(value,2))

@@

  plotData <- df %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>%
    mutate(value = round(value,2))

@@

  plotData <- df %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>%
    mutate(sector = factor(invertVars[as.character(variable)], c("Total", "Transport", "Industry", "Buildings"))) %>%
    mutate(value = round(value,4))

@@

  plotData <- df %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% unlist(vars)) %>%
    mutate(type = gsub("\\d$", "", as.character(invertVars[as.character(variable)]))) %>%
    group_by(model,scenario,region,unit,period,type,tgt2030,lim) %>%
    summarize(value=sum(value),.groups = "keep") %>%
    mutate(type=factor(type, levels=unique(gsub("\\d$", "", names(vars))))) %>%
    mutate(value = round(value,2))

@@

  plotData <- df %>%
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(value = round(value,2))

@@

  plotData <- df %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(sector = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value,2))

@@

  plotData <- df %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(pe = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value,2))

@@

  plotData <- df %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(seel = factor(invertVars[as.character(variable)], names(vars))) %>%
    mutate(value = round(value * 1/0.0036))

@@

<!--   plotData <- df %>%  -->
<!--     filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>% -->
<!--     calc_addVariable( "`emiIntTrnsp`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr") %>% -->
<!--     calc_addVariable( "`emiIntraEU`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr") %>% -->
<!--     filter(variable %in% c("emiIntTrnsp","emiIntraEU")) %>% -->
<!--     pivot_wider(names_from = variable, values_from = value) %>% -->
<!--     mutate(ref_emiIntTrnsp = tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference), -->
<!--            ref_emiIntraEU = tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) %>% -->
<!--     mutate(red_emiIntTrnsp = emiIntTrnsp/ref_emiIntTrnsp, -->
<!--            red_emiIntraEU = emiIntraEU/ref_emiIntraEU) %>% -->
<!--     mutate(value = emiIntTrnsp, -->
<!--            reduction = ifelse(period >= 2045, red_emiIntTrnsp, red_emiIntraEU)) %>% -->
<!--     mutate(text = paste0("Emissions: ", round(value), " Mt CO2/yr", "\nReduction: ", round(1-reduction,3)*100, "%", "\nPeriod: ", period, "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim)) %>% -->
<!--     mutate(value = round(value,2)) -->

@@

<!-- # # Final Energy -->
<!-- # vars <- c( -->
<!-- #   "Electricity" = "FE|Electricity", -->
<!-- #   "Heat" = "FE|Heat", -->
<!-- #   "Hydrogen" = "FE|Hydrogen", -->
<!-- #   "Gases" = "FE|Gases", -->
<!-- #   #"Gases" = "FE|Gases|Biomass", -->
<!-- #   #"Gases" = "FE|Gases|Hydrogen", -->
<!-- #   #"Gases" = "FE|Gases|Fossil", -->
<!-- #   "Liquids" = "FE|Liquids", -->
<!-- #   #"Liquids" = "FE|Liquids|Biomass", -->
<!-- #   #"Liquids" = "FE|Liquids|Hydrogen", -->
<!-- #   #"Liquids" = "FE|Liquids|Fossil", -->
<!-- #   "Solids" = "FE|Solids"	 -->
<!-- #   #"Solids" = "FE|Solids|Biomass",	 -->
<!-- #   #"Solids" = "FE|Solids|Fossil"	 -->
<!-- # ) -->
<!-- #  -->
<!-- # invertVars <- setNames(names(vars),vars) -->
<!-- #  -->
<!-- # plotData <- df %>%  -->
<!-- #   filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen, variable %in% vars) %>% -->
<!-- #   mutate(fe = factor(invertVars[as.character(variable)], names(vars))) -->
<!-- #  -->
<!-- # g[["finalEnergy"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) + -->
<!-- #     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
<!-- #     geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
<!-- #     geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario)) + -->
<!-- #     facet_wrap(~ fe, nrow=2) + -->
<!-- #     scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) +  -->
<!-- #     scale_color_manual(values = scenarioColor) +  -->
<!-- #     scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) + -->
<!-- #     scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) + -->
<!-- #     theme_doubleColumn() + -->
<!-- #     theme(legend.position = "none") + -->
<!-- #     theme(axis.title.y=element_blank())  -->
<!-- #  -->
<!-- # plotly2js( -->
<!-- #   ggplotly(ggplotly(g[["finalEnergy"]])) %>% layout(autosize = TRUE), -->
<!-- #              div.id = "finalEnergy", output.html = TRUE, output.file = "finalEnergy.js",  -->
<!-- #              output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/finalEnergy.html")) -->
